On the characteristic and diameter of planar integral point sets \footnote{ The work of the first author was partially supported by the Theoretical Physics and Mathematics Advancement Foundation “BASIS”. }

### 2025-08-24 char-4k-bound/char-4k-bound.tex
[4k3][typos]

\section{Acknowledgements}
The author thanks Dr. Prof. E.M. Semenov for the fruitful discussion and ideas,
Dr. A.S. Chervinskaia for the idea of using the term ``facher'' and proofreading,
Dr.~A.S.~Usachev for proofreading,
and E.A. Momot for the ``SciLexic'' project that helped the author with some word usage issues.
Also the author would like to owe a special thanks to the anonymous referees
for their helpful comments and suggestions on the paper.

>>>>

\section{Acknowledgements}
The authors thank Dr. Prof. E.M. Semenov for the fruitful discussion and ideas,
Dr. A.S. Chervinskaia for the idea of using the term ``facher'' and proofreading,
Dr.~A.S.~Usachev for proofreading,
and E.A. Momot for the ``SciLexic'' project that helped the authors with some word usage issues.
Also the authors would like to owe a special thanks to the anonymous referees
for their helpful comments and suggestions on the paper.
